THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-04-14 DishReflectometry/Paper1_v1.tex
Proofreading and sharping
Basic proofreading, grammer checking, and sharping of sentence structure.

One of the most problematic effects facing these experiments is instrument
chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
importance; for line emission, this coordinate translates to a line-of-sight distance
that can be used to construct three-dimensional maps (and power spectra) of emission,
as well as probe the evolution of 21~cm emission over cosmological timescales.
The evolving response of a radio telescope --- either a single dish
or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds,
contaminating spectral modes that might
otherwise be used to measure reionization ~\citep{XXX}.  Moreover, the chromaticity of
a telescope's response scales linearly with diameter, putting the
needs of foreground suppression and signal sensitivity in direct tension with one
another. In addition to that, systematic effects are unique to each instruments and their manifestation 
is different in each dataset.

A major step forward for the field of 21~cm cosmology has been the development
of a mathematical description of telescope chromaticity, how it varies with
element separation (or telescope diameter), and what it implies for distinguishing
foreground emission from the cosmological 21~cm signal ~\citep{XXX}.  The ``wedge'', as it is
colloquially known, describes a linear relationship between the separation between elements
in an interferometric baseline and the maximum line-of-sight Fourier mode\footnote{Assuming
a flat sky, and using appropriate
cosmological scalars,
the spectral axis, $\nu$, and angle on the sky, $\vec\theta$, translate to coordinates in
a three-dimensional volume at cosmological distances.  In describing the spatial power spectrum of
emission in this volume $P(\vec k)$, we use the three-dimensional wave vector 
$\vec k\equiv(k_\parallel,\vec k_\perp)$, where $k_\parallel$ is aligned with the
spectral axis $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
that may be occupied by smooth spectrum foreground emission.  At low-order $k_\parallel$ modes
within the limits of the wedge,
foreground contamination may be suppressed through a combination of calibration and model 
subtraction.  However, calibration or modeling errors rapidly re-establish the characteristic
wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
~\citep{pober_et_al2013,thargarajan_et_al2015}, provided that the spectral responses
of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
the chromaticity of the elements in isolation from the chromaticity inherent to
element separation in an interferometric baseline.}.  In promising avoidance-based
foreground strategy employed by PAPER ~\citep{parsons_et_al2014,ali_et_al2015}, these modes
may be targeted as the lowest risk path for contraining 21~cm reionization in the near term.

% XXX document map
The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  ~\citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length. Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. 
Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\ 
The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scale will be lost.

The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
In this paper, we investigate the performance of an individual HERA element and resulting contribution of the instrument response to the delay spectrum.
 Reflectometry measurements  are carried out across wide bandwidth on a prototype HERA element in Green
Bank, WV (Figure \ref{fig:heradish}) and the results are interpreted in the light of delay spectrum technique. Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer. Reflectometry measurements are described in section 3. Section 4 describes the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.
In coordination with ~\citet{XXXsisterpapers}, we compare 
reflectometry measurements with
a specification for the spectral performance of an element, given models of the relative brightness of
foreground and 21~cm reionization modes in $k$-space in section 5.

@@

\section{Visibility measurements by a two element interferometer and the delay spectrum}
Consider a two element interferometer with a baseline $\vec b$. If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$  then the voltage output of each antenna may be written as,  
\begin{equation}
\volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)\volt_\sky(\thhat,\nu)\nonumber\\
\end{equation}
\begin{equation}
\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
\end{equation}
Hence, the time averaged visibility measured by the interferometer may be written as, 
\begin{equation}
\vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)  \volt_{2}^{*} (\thhat, \nu) \ifngexp d\Omega 
\label{eq1}
\end{equation}

We define antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$. Hence, 
\begin{equation}
\vis(\vec b,\nu) = \int \beam(\thhat, \nu) I_\sky(\thhat,\nu) \ifngexp d\Omega
	%	& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
 	%	& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
	%	& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
	%	& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
\label{eq2}
\end{equation}

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
The redshifted 21 cm spatial power spectrum is defined as
\begin{equation}
  P(k_\perp,k_\parallel) = |\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\label{eq:delay-power-spectrum}
\end{equation}
where
\begin{equation}
  k_\perp = \frac{2\pi f}{D}({b\over c}), \\
  k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
\end{equation}
The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
$f_{21}$:rest frame frequency of the 21~cm radiation.\\
$f$: observation frequency.\\
$z$: cosmological redshift corresponding to frequency of observation.\\
 $\Delta B$: bandwidth centered at the observation frequency.\\
 $k_\textrm{B}$: Boltzmann constant.\\
 $D\equiv D(z)$ comoving distance along the line of sight\\
 $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
$E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\

In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay $\tau$ corresponding to the given baseline length, the redshifted 21 cm power spectrum could be estimated from the measurement of delay spectrum of visibility by an interferometer. Sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
 in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $P_{sky}(\tau)$ is contributed by the foreground  $P_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $P_{21}(\tau)$ which contains spectral signatures.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could be detectable.

 %In words, the sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.

@@

\section{Effects of multiple reflections on visibility and delay spectrum}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER. Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it is reflected back into the space.
However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum. 
In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum, using the multiple reflection formulation of Sec. \ref{sec:multiple}. In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed in detail. We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{Antenna Reception With Multiple Reflections}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig. \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
\caption{System}
\label{fig:sys}
\end{figure}

\noindent
%Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
Hence,
 \begin{eqnarray}
{\volt_{rec}\over \volt_{sky} } & = &   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}\nonumber\\
& = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} 
 \label{eq:Sigma}
\end{eqnarray}
Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).  We may identify $(1+\Gamma_d)(1+\Gamma_{a})$ as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.  Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).

@@

The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna. Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.  The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line. The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.

@@

\caption{Complex antenna impedance of the HERA feed element.}

@@

\subsubsection{Effect of dish and the feed on delay spectrum estimation}

>>>>

One of the most problematic effects facing these experiments is instrument
chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
importance; for line emission, this coordinate translates to a line-of-sight distance
that can be used to construct three-dimensional maps (and power spectra) of emission,
as well as probe the evolution of 21~cm emission over cosmological timescales.
The evolving response of a radio telescope --- either a single dish
or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds,
contaminating spectral modes that might
otherwise be used to measure reionization ~\citep{XXX}.  Moreover, the chromaticity of
a telescope's response scales linearly with diameter, putting the
needs of foreground suppression and signal sensitivity in direct tension with one
another. In addition to that, systematic effects are unique to each instrument and their manifestation 
is different in each dataset.

A major step forward for the field of 21~cm cosmology has been the development
of a mathematical description of telescope chromaticity, how it varies with
element separation (or telescope diameter), and what it implies for distinguishing
foreground emission from the cosmological 21~cm signal ~\citep{XXX}.  The ``wedge'', as it is
colloquially known, describes a linear relationship between the separation between elements
in an interferometric baseline and the maximum line-of-sight Fourier mode\footnote{Assuming
a flat sky and using appropriate
cosmological scalars,
the spectral axis, $\nu$, and angle on the sky, $\vec\theta$, translate to coordinates in
a three-dimensional volume at cosmological distances.  In describing the spatial power spectrum of
emission in this volume $P(\vec k)$, we use the three-dimensional wave vector 
$\vec k\equiv(k_\parallel,\vec k_\perp)$, where $k_\parallel$ is aligned with the
spectral axis, $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
that may be occupied by smooth spectrum foreground emission.  At low-order $k_\parallel$ modes
within the limits of the wedge,
foreground contamination may be suppressed through a combination of calibration and model 
subtraction.  However, calibration or modeling errors rapidly re-establish the characteristic
wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
~\citep{pober_et_al2013,thargarajan_et_al2015}, provided that the spectral responses
of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
the chromaticity of the elements in isolation from the chromaticity inherent to
element separation in an interferometric baseline.}.  In the promising, avoidance-based
foreground strategy employed by PAPER ~\citep{parsons_et_al2014,ali_et_al2015}, these modes
may be targeted as the lowest risk path for constraining 21~cm reionization in the near term.

% XXX document map
The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  ~\cite{ParsonsBacker2009,Parsons2012}, computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as the delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across a wide frequency bandwidth, the delay spectrum consists of the instrument response, the foreground signal, and the 21cm power spectrum, hereafter referred to as the EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay, $\tau = b/c$, corresponding to the given baseline length. Such techniques also assume a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. 
Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuations over small scales, such as the EoR signal, and therefore, could be detectable.\\
\indent The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and, thus, influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over into higher delays and, thus, push the upper limit of the foreground and systematics contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scales will be lost. \\
\indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
In this paper, we investigate the performance of an individual HERA element and the resulting contribution of the instrument response to the delay spectrum.
 Reflectometry measurements  are carried out across a wide bandwidth on a prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the results are interpreted in light of the delay spectrum technique. Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer. Reflectometry measurements are described in section 3. Section 4 describes the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.
In coordination with ~\citet{XXXsisterpapers}, we compare 
reflectometry measurements with
a specification for the spectral performance of an element, given models of the relative brightness of
foreground and 21~cm reionization modes in $k$-space in section 5.

@@

\section{Visibility measurements by a two element interferometer and the delay spectrum}
Consider a two element interferometer with a baseline $\vec b$. If we denote the electric field sky signal in the direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,  
\begin{equation}
\volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)\volt_\sky(\thhat,\nu)\nonumber\\
\end{equation}
\begin{equation}
\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
\end{equation}
Hence, the time averaged visibility measured by the interferometer may be written as, 
\begin{equation}
\vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)  \volt_{2}^{*} (\thhat, \nu) \ifngexp d\Omega 
\label{eq1}
\end{equation}

We define the antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$. Hence, 
\begin{equation}
\vis(\vec b,\nu) = \int \beam(\thhat, \nu) I_\sky(\thhat,\nu) \ifngexp d\Omega
	%	& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
 	%	& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
	%	& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
	%	& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
\label{eq2}
\end{equation}

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spectrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
The redshifted 21 cm spatial power spectrum is defined as
\begin{equation}
  P(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
\label{eq:delay-power-spectrum}
\end{equation}
where
\begin{equation}
  k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
  k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
\end{equation}
The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
$f_{21}$:rest frame frequency of the 21~cm radiation.\\
$f$: observation frequency.\\
$z$: cosmological redshift corresponding to the frequency of observation.\\
 $\Delta B$: bandwidth centered at the observation frequency.\\
 $k_\textrm{B}$: Boltzmann constant.\\
 $D\equiv D(z)$ comoving distance along the line of sight\\
 $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
$E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
\indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay $\tau$, corresponding to the given baseline length, the redshifted 21 cm power spectrum could be estimated from the delay spectrum of the visibility measured by an interferometer. The sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
 in the delay domain. The maximum geometric delay possible for a given baseline would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$, when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to the chromaticity of the sky signal as well as the instrument response, the delay spectrum of the sky spills over into delays with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12]. The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the sky delay spectrum, $P_{sky}(\tau)$.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground, with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay spectrum could be detectable.

 %In words, the sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the Figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.

@@

\section{Effects of multiple reflections on visibility and delay spectrum}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment, PAPER. Plane waves incident on a parabolic dish are focussed at the feed, which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it reflects back into free space.
However, a part of it is reflected back and forth several times in between the feed and the vertex of the dish, which is shadowed by the feed. %No longer an included figure (dashed blue arrows in Figure \ref{fig:cartoon}).
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delays and phases and, thus, produce spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could result from reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of the 21cm power spectrum. \\
\indent In this section, we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding affects on the delay spectrum, using the multiple reflection formulation of Sec. \ref{sec:multiple}. We also examine, in detail, the affect of reflections on the visibility data and the corresponding affect on the delay spectrum. We assume two antennas with identical geometry and electrical parameters, i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{Antenna Reception With Multiple Reflections}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, we can think of the system as a screen at a distance $F$ from a feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally, however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
\caption{System}
\label{fig:sys}
\end{figure}

\noindent
%Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
Hence,
 \begin{eqnarray}
{\volt_{rec}\over \volt_{sky} } & = &   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}\nonumber\\
& = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} 
 \label{eq:Sigma}
\end{eqnarray}
Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).  We may identify $(1+\Gamma_d)(1+\Gamma_{a})$ \textbf{Shouldn't have $\mathbf{(1+\Gamma_a)}$?} as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.  Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).

@@

The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed. Additionally, with each reflection, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since the reflected signal results in a system response at a higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum. The return loss of power results from the antenna impedance mismatch with free space as well as the transmission line. The complex antenna impedance is shown in Figure \ref{fig:feed_impedance}.

@@

\caption{Complex antenna impedance of the HERA feed element.} %Some indication of which line is which on the plot would be really helpful here.

@@

\subsubsection{Effect of the dish and feed on the delay spectrum estimation}
